On the eletrodynamic of moving bodies

### 2019-06-03 Article_AS.Rmd
Discussion1

The data set showed a typical radial pattern of wood density already observed in spruce trees in other studies [@Alteyrac2006; @GARDINER2011; @Xiang2014]. The trend is similar to that described as Type II density profile in @panshin1980. The high density during the first years of tree growth can be explained by the immature tracheids combined with the high proportion of compression wood. The density decreases to a certain level and begins to increase again. This increase is due to the fact that the width of the ring decreases from a certain age, so the proportion of initial decreases and that of the final wood [@Lachenbruch2011]. 
The difference between the two sites at the parameter level can be explained by the fact that the climate between these sites is not the same which influences the variation of the density. 
The modeling of individual profiles is suitable for the description of the wood density of our type II data. The choice of model allowed to take into account the variability of the density profiles of white spruce.  @Xiang2014 applied a similar model in their study to describe the density profiles of black spruce with density profiles similar to those of white spruce. The low index of parameters $b_1$ and $b_2$ were most likely the large variability of the initial decline near the pith.
The index of variability is different between the two sites, despite the fact that they are the same families of trees. This can be explained by the fact that both sites have different climatic conditions. It would be environmental. The fact that the index of variability is more under environmental control than genetic explains the lack of heritability of this index. It is not surprising that the variability index is under environmental control because it is calculated from model residuals. The model has made it possible to subtract the typical trend of the variation of the density which is related to the internal functioning of the tree [@Lachenbruch2011] and thus under genetic control. Once the portion of the variation under genetic control is subtracted, the rest of the variability can only be of a pedoclimatic order.
As for Spearman's rank correlation coefficient is not significant (p-value = 0.43; rho = 0.08) for the index of variability. This coefficient value is in agreement with the previous results which show a difference between the two sites and the fact that the variability index is under environmental control. The similarity of the correlation coefficient between the three parameters is explained by the fact that the model adapts well to each of the two sites taking into account the extreme variability of the different density profiles.
Heritability of density is high at both sites. This strong density heritability is similar to previous studies in white spruce [@Corriveau1991; @Yanchuk1993; @Ivkovich2002a; @Ivkovich2002b; @Beaulieu2006]. All of these studies reported values between 0.36 and 0.52. 
In contrast to density, annual ring width has low to moderate heritability in each site and also for combined sites. This result, which is in agreement with previous studies [@Corriveau1991; @Ivkovich2002a], is explained by the fact that growth is more influenced by environmental conditions than by genetics. The difference we observe when we take the sites separately and when they are combined can be explained by a genotype-environment interaction [@kremer1986].
The parameters of the model, as for them, they have a low heritability either for each site separately or for the combined sites. The parameter b0, has a higher heritability than the other parameters but remains low. This can be explained by the fact that this parameter is very little influenced by cambial age.
The index of variability has almost no heritability. It is not surprising that this trait has very low heritability because it is estimated from model residuals after subtracting the typical density profile.
Our study includes limitations for identifying families that may have low variability in wood density as part in tree improvement programs. Future studies should focus on the resilience and variability associated with one-time events such as short-term water stress. In addition, the trees used for this study are relatively young, we can be interested in older trees.

>>>>

The data set showed a typical radial pattern of wood density already observed in spruce trees in other studies [@Alteyrac2006; @GARDINER2011; @Xiang2014]. The trend is similar to that described as Type II density profile in @panshin1980. The high density during the first years of tree growth can be explained by the immature tracheids combined with the high proportion of compression wood. The density decreases to a certain level and begins to increase again. This increase is due to the fact that the width of the ring decreases from a certain age, so the proportion of initial decreases and that of the final wood [@Lachenbruch2011]. 
The modeling of individual profiles is suitable for the description of the wood density of our type II data. The choice of model allowed to take into account the variability of the density profiles of white spruce. @Xiang2014 applied a similar model in their study to describe the density profiles of black spruce with density profiles similar to those of white spruce. The low index of parameters $b_1$ and $b_2$ were most likely the large variability of the initial decline near the pith. Although the variaton of density follows a Type II profile, it remains slightly different between the two sites. This difference can be explained by the difference in pedoclimatic cinditions between sites. Although, the soil type is different between sites and the climate is colder in Asselin compared to Saint-Casimir. At the level of the model parameters, the sites are also different and this difference can be explained by the profiles of densities that are not the same.\

The index of variability is different between two sites, despite the fact that they are the same families of trees. Since the variability index is calculated from the model residuals, the difference can be explained by the fact that the variability that is related to the internal control of the trees has been subtracted from the model and that the remaining one is more controlled by external phenomena related to the study sites. The fact that the index of variability is more under environmental control than genetic explains the lack of heritability of this index. It is not surprising that the variability index is under environmental control because density is mainly controlled by genetics but partly also by growth that is mainly controlled by environmental conditions. The model has made it possible to subtract the typical trend of the variation of the density which is related to the internal functioning of the tree [@Lachenbruch2011] and thus under genetic control. Once the portion of the variation under genetic control is subtracted, the rest of the variability can only be of a pedoclimatic order.\

The index of variability being different between the sites, as one would expect Spearman's rank coefficient of correlation is not significant (p-value = 0.43; rho = 0.08) for this index. This coefficient value is in agreement with the previous results which show a difference between the two sites and the fact that the variability index is under environmental control. The similarity of the correlation coefficient between the three parameters is explained by the fact that the model adapts well to each of the two sites taking into account the extreme variability of the different density profiles.\

Heritability of density is high at both sites. This strong density heritability is similar to previous studies in white spruce [@Corriveau1991; @Yanchuk1993; @Ivkovich2002a; @Ivkovich2002b; @Beaulieu2006]. All of these studies reported values between 0.36 and 0.52. 
In contrast to density, annual ring width has low to moderate heritability in each site and also for combined sites. This result, which is in agreement with previous studies [@Corriveau1991; @Ivkovich2002a], is explained by The difference we observe when we take the sites separately and when they are combined can be explained by a genotype-environment interaction [@kremer1986], this happens when conditions from one environment to another do not have the same effect on the genotype. This result suggests that, if trees are to be selected for reforestation as a result of this study, the territory be divided into relatively homogeneous subunits, within which the recommended sources will be able to keep their superiority and can be used without risk of maladjustment [@beaulieu1989stabilite].

The parameters of the model, as for them, they have a low heritability either for each site separately or for the combined sites. The parameter $b_0$, has a higher heritability than the other parameters but remains low. This can be explained by the fact that this parameter is very little influenced by cambial age. In fact, $b_0$ is the ordinate at the origin and thus little influenced by the sites (environmental conditions).
The index of variability has almost no heritability. It is not surprising that this trait has very low heritability because it is estimated from model residuals after subtracting the typical density profile.
Our study includes limitations for identifying families that may have low variability in wood density as part in tree improvement programs. Future studies should focus on the resilience and variability associated with one-time events such as short-term water stress. In addition, the trees used for this study are relatively young, we can be interested in older trees.
